\textbf{EECS 340: Assignment 3}

### 2020-02-21 assignment_3/article.tex
🐛 💄 Fix Q2(a) sign typo on induction W.T.S. (from = to <=).

\paragraph{Given $T(n) = T(\alpha n) + T((1-\alpha)n) + \Theta(n)$\newline}
\begin{proof}
We may rewrite it as $T(n) = T(\alpha n) + T((1-\alpha)n) + dn$ for $d \in \mathbb{Z^+}$. Assume the claim $T(k) = ck \log k - c'k$ holds true for $T(k)$ for $k \in [1, n)$, and without loss of generality assume that $\alpha \geq 0.5$, we have:

>>>>

\paragraph{Given $T(n) = T(\alpha n) + T((1-\alpha)n) + \Theta(n)$\newline}
\begin{proof}
We may rewrite it as $T(n) = T(\alpha n) + T((1-\alpha)n) + dn$ for $d \in \mathbb{Z^+}$. Assume the claim $T(k) \leq ck \log k - c'k$ holds true for $T(k)$ for $k \in [1, n)$, and without loss of generality assume that $\alpha \geq 0.5$, we have:
